Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-05 nakayama/paper.tex
Changed en dashes to em.

% Mention an attempt with modules
% Formalizing algebra => crypto
% Interesting steps of the proof
% ssreflect still looks to only deal with finite/discrete objects

@@

The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.  Research in the field now centers around \emph{commutative rings}--rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$--and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them. 
Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.

@@

Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields--commutative rings in which every nonzero element has a multiplicative inverse--such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.

@@

\subsection{Formal Proof of Nakayama's Lemma}

\begin{theorem}[Nakayama's lemma]
  Let \(M\) be a finitely generated module over a local ring \(R\) with maximal
  ideal \(\mathfrak{m}\). If \(\mathfrak{m} M = M\), then \(M = 0\), which is
  to say that \(M\) is the zero module which consists of exactly one element,
  that being the zero vector.
\end{theorem}

>>>>

% Mention an attempt with modules
% ssreflect still looks to only deal with finite/discrete objects

@@

The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.  Research in the field now centers around \emph{commutative rings}---rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them. 
Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.

@@

Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields---commutative rings in which every nonzero element has a multiplicative inverse---such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.

@@

\subsection{Formal Proof of Nakayama's Lemma}
\begin{theorem}[Nakayama's lemma]
  Let \(M\) be a finitely generated module over a local ring \(R\) with maximal
  ideal \(\mathfrak{m}\). If \(\mathfrak{m} M = M\), then \(M = 0\), which is
  to say that \(M\) is the zero module which consists of exactly one element,
  that being the zero vector.
\end{theorem}
